---
title: "經濟實證與預測三HW1"
author: "Jinze Wu"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# E6.2
Using the data set Growth described in Empirical Exercise E4.1, but excluding the data for Malta, carry out the following exercises.
```{r}
growth <- read.csv("Econometrics 4e Data Files/Growth (EE 4.1, 5.2, 6.2)/Growth.csv")
growth <- subset(growth, country_name != 'Malta')  # Exclude "Malta"
head(growth)
```

a. Construct a table that shows the sample mean, standard deviation, and minimum and maximum values for the series Growth, TradeShare, YearsSchool, Rev_Coups, Assassinations, and RGDP60. Include the appropriate units for all entries.
```{r}
# mean, standard deviation, minimum, maximum
# growth, tradeShare, yearsSchool, rev_Coups, assassinations, rgdpP60
mean(growth$growth)
mean(growth$rgdp60)
sd(growth$growth)
sd(growth$rgdp60)
min(growth$growth)
min(growth$rgdp60)
max(growth$growth)
max(growth$rgdp60)
```

b. Run a regression of Growth on TradeShare, YearsSchool, Rev_Coups, Assassinations, and RGDP60. What is the value of the coefficient on Rev_Coups? Interpret the value of this coefficient. Is it large or small in a real-world sense?

```{r}
model <- lm(growth~tradeshare+yearsschool+rev_coups+assasinations+rgdp60, data=growth)
summary(model)
```
```
The value of the coefficient on Rev_Coups is -2.15, and statistically significant.
其他條件不變化，若政變次數增加 1 次，平均而言，平均年GDP成長率將下降2.15個百分點。
2020年台灣GDP成長率 3.11%, so it is large in a real-world sense.
```

c. Use the regression to predict the average annual growth rate for a country that has average values for all regressors.
```{r}
myData <- data.frame(
  tradeshare=mean(growth$tradeshare),
  yearsschool=mean(growth$yearsschool),
  rev_coups=mean(growth$rev_coups),
  assasinations=mean(growth$assasinations),
  rgdp60=mean(growth$rgdp60))
predict(model, myData)
```

d. Repeat (c), but now assume that the country’s value for TradeShare is one standard deviation above the mean.
```{r}
myData <- data.frame(
  tradeshare=mean(growth$tradeshare)+sd(growth$tradeshare),  # one standard deviation above the mean
  yearsschool=mean(growth$yearsschool),
  rev_coups=mean(growth$rev_coups),
  assasinations=mean(growth$assasinations),
  rgdp60=mean(growth$rgdp60))
predict(model, myData)
```

e. Why is Oil omitted from the regression? What would happen if it were included?
```
貢獻性問題
```
