---
title: "經濟實證與預測三HW1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(readxl)
library(lmtest)
library(sandwich)
```

# E6.2

Using the data set **Growth** described in Empirical Exercise E4.1, but excluding the data for Malta, carry out the following exercises.

```{r, include=FALSE}
setwd("~/Econometrics 4e Data Files/Growth (EE 4.1, 5.2, 6.2)")
growth <- read_excel("Growth.xlsx")
growth <- subset(growth, country_name != "Malta")  # Exclude "Malta"
```

(a) Construct a table that shows the sample mean, standard deviation,
and minimum and maximum values for the series *Growth*, *TradeShare*, *YearsSchool*, *Rev_Coups*, *Assassinations*, and *RGDP60*. Include the
appropriate units for all entries.

```{r, include=FALSE}
growth_mean <- c(mean(growth$growth), mean(growth$tradeshare), mean(growth$yearsschool), mean(growth$rev_coups), mean(growth$assasinations), mean(growth$rgdp60))

growth_sd <- c(sd(growth$growth), sd(growth$tradeshare), sd(growth$yearsschool), sd(growth$rev_coups), sd(growth$assasinations), sd(growth$rgdp60))

growth_min <- c(min(growth$growth), min(growth$tradeshare), min(growth$yearsschool), min(growth$rev_coups), min(growth$assasinations), min(growth$rgdp60))

growth_max = c(max(growth$growth), max(growth$tradeshare), max(growth$yearsschool), max(growth$rev_coups), max(growth$assasinations), max(growth$rgdp60))

row_name = c('growth(%)', 'tradeshare(%)', 'yearsschool(Average annual number of years)', 'rev_coups(Average annual number of revolutions)', 'assasinations(Average annual number of political assassinations)', 'rgdp60(1960 US dollars)')

df <- data.frame(mean=growth_mean, sd=growth_sd, min=growth_min, max=growth_max, row.names=row_name)

```

```{r, echo=FALSE}
df
```

(b) Run a regression of *Growth* on *TradeShare*, *YearsSchool*, *Rev_Coups*, *Assassinations*, and *RGDP60*. What is the value of the coefficient on *Rev_Coups*? Interpret the value of this coefficient. Is it large or small in
a real-world sense?

```{r, echo=FALSE}
model <- lm(growth~tradeshare+yearsschool+rev_coups+assasinations+rgdp60, data=growth)

# Robust t test
coeftest(model, vcov = vcovHC(model, type = "HC1"))
```

```
The value of the coefficient on Rev_Coups is 2.15
若政變次數增加 1 次，平均而言，平均年GDP成長率將下降2.15個百分點。
2020年台灣GDP成長率 3.11%, so it is large in a real-world sense.
```

(c) Use the regression to predict the average annual growth rate for a
country that has average values for all regressors.

```{r, echo=FALSE}
predictdata <- data.frame(
  tradeshare=mean(growth$tradeshare),
  yearsschool=mean(growth$yearsschool),
  rev_coups=mean(growth$rev_coups),
  assasinations=mean(growth$assasinations),
  rgdp60=mean(growth$rgdp60)
)
predict(model, newdata = predictdata)
```


```
The average annual growth rate is 1.87%
```

(d) Repeat (c), but now assume that the country’s value for *TradeShare* is
one standard deviation above the mean.

```{r, echo=FALSE}
predictdata <- data.frame(
  tradeshare=mean(growth$tradeshare)+sd(growth$tradeshare),
  yearsschool=mean(growth$yearsschool),
  rev_coups=mean(growth$rev_coups),
  assasinations=mean(growth$assasinations),
  rgdp60=mean(growth$rgdp60)
)
predict(model, newdata = predictdata)
```

```
The average annual growth rate is 2.175%
```

(e) Why is *Oil* omitted from the regression? What would happen if it were
included?

```
由於 Oil 資料皆為 0 ，若放入迴歸式，將與常數項產生共線性問題，
導致估計出現偏誤。
```
